### 2017-06-22 paper/compositional.tex
preparing to adjust the definition of pCFG

Let $\program$ be a \PP{} of the form $\textbf{while } \Psi \textbf{ do } 
\programbody \textbf{ od}$. We denote by $\loops(\program)$ the set of all 
loops in $\program$ there are on the top level of $\programbody$, i.e. they are 
nested loops of $\program$ nested directly "below" the outer loop. We define a 
depth-1 slice of $\program$ to be a \PP{} $\slice(\program)$ obtained from 
$\program$ by removing all loops in $\loops(\program)$. A formal definition of 
both functions is given in \AppendixMaterial, we illustrate them in the 
following example.

@@

>>>>

Let $\program$ be a \PP{} of the form $\textbf{while } \Psi \textbf{ do } 
\programbody \textbf{ od}$. We denote by $\loops(\program)$ the set of all 
loops in $\program$ there are on the top level of $\programbody$, i.e. they are 
nested loops of $\program$ nested directly "below" the outer loop. We define an 
un-nested slice of $\program$ to be a \PP{} $\slice(\program)$ obtained from 
$\program$ by removing all loops in $\loops(\program)$ and replacing them with 
skip statements. We also define the set 
$\alloops(\program)$ of all loops in $\program$, i.e. 
$\alloops(\program):=\loops(\program)\cup \{\loops(\program')\mid \program'\in 
\loops(\program)\}$. A 
formal definition of 
both functions is given in \AppendixMaterial, we illustrate them in the 
following example.

@@

\textbf{[PETR: INTRODUCE SETS OF INITIAL PROGRAM VALUATIONS RATHER THAN A 
CONCRETE VALUATION]}

Each measurable map for $\lem$ can be, in a natural way, restricted to a 
measurable map $\lem_{\program'}$ for $\program'\in \loops(\program)$, 
since each pCFG $\pCFG_{\program'}$ is a sub-pCFG of $\pCFG_{\program}$. 
Similarly, a measurable map $\lem$ for $\program$ can be restricted to a 
measurable map $\lem_{\slice}$ for $\slice(\program)$, since 
$\pCFG_{\slice(\program)}$ is produced from $\pCFG_{\program}$ essentially by 
removing certain locations (provided that we identify the locations forming 
heads of nested loops with locations preceding skip statements), and 
$\lem_{\slice}$ is defined to be equal to $\lem$ in all the locations that 
remained.
